Maps

### 2016-03-21 108-mapping.Rmd
Count number of sections for comparison to NY

```{r}
library(dplyr)
library(stringr)
library(textreuse)
library(readr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
```

@@

map_matches <- map_matches %>% 
  filter(borrower_year >= match_year) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup() %>%  
  filter(score >= 0.2)

@@

map_summary <- map_matches %>% 
  group_by(borrower_state) %>% 
  summarize(score = mean(score)) %>% 
  arrange(desc(score)) 
```

```{r}
library(ggplot2)
library(broom)
library(USAboundaries)
library(rgeos)
library(maptools)
library(scales)
us <- us_states()
us_fortified <- tidy(us, region = "stusps") %>% 
  left_join(map_summary, by = c("id" = "borrower_state")) %>% 
  filter(id != "AK",
         id != "HI",
         id != "PR")

ggplot() +
  geom_polygon(data = us_fortified,
               aes(x = long, y = lat, group = group, fill = 1 - score),
               color = "black", size = 0.25) +
  scale_fill_distiller(name = "Avg. dissimilarity score", palette = "YlGn",
                       breaks = pretty_breaks(n = 5)) +
  coord_map("albers", lat0=30, lat1=40) +
  theme_classic() +
  labs(title = "Strength of borrowings from Field Code",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.position = "bottom")
```

@@

>>>>

```{r}
library(dplyr)
library(stringr)
library(textreuse)
library(readr)
load("cache/corpus-lsh.rda")
source("R/helper.R")
list1 <- read_lines("compare-to-NY-list-1.txt")
list2 <- read_lines("compare-to-NY-list-2.txt")
library(classInt)
```

@@

regions <- read_csv("regions.csv")

map_matches_sections <- map_matches %>% 
  filter(borrower_year >= match_year) %>% 
  group_by(borrower_section) %>% 
  arrange(desc(score)) %>% 
  slice(1) %>% 
  ungroup() %>%  
  filter(score >= 0.2) %>% 
  count(borrower_code) %>% 
  mutate(year = extract_date(borrower_code)) %>% 
  mutate(state = extract_state(borrower_code)) %>% 
  left_join(regions)

@@

map_summary <- map_matches %>% 
  # filter(borrower_code %in% list2) %>% # Just the codes Kellen picked
  group_by(borrower_state) %>%
  summarize(score = sum(score)) %>% 
  arrange(desc(score))

intervals <- classIntervals(map_summary$score, n = 5, style = "jenks")
map_summary$score <- cut(map_summary$score, breaks = intervals$brks)
```

```{r}
library(ggplot2)
library(broom)
library(USAboundaries)
library(rgeos)
library(maptools)
library(scales)
library(RColorBrewer)
us <- us_states()
us_fortified <- tidy(us, region = "stusps") %>% 
  left_join(map_summary, by = c("id" = "borrower_state")) %>% 
  filter(id != "AK",
         id != "HI",
         id != "PR")

ggplot() +
  geom_polygon(data = us_fortified,
               aes(x = long, y = lat, group = group, fill = score),
               color = "black", size = 0.25) +
  scale_fill_manual("Avg. dissimilarity score", values = brewer.pal(5, "YlGn")) +
  coord_map("albers", lat0=30, lat1=40) +
  theme_classic() +
  labs(title = "Strength of borrowings from Field Code (List 2)",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        legend.position = "bottom")
```

@@

```{r}
library(ggrepel)
ggplot(map_matches_sections, aes(x = year, y = n, color = region, group = state)) +
  geom_point() +
  geom_line() 
    # geom_label_repel(aes(label = state))
```
